### 2016-03-14 paper/result_layered_depthmap.tex
yasu

\mysubsubsection{Layered Depthmap}

\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/layered_depthmap_convergence.png}
  \caption{The energy minimization process for layered depthmap estimation of different methods. Multi-way fusion is shown to be more effectvie than binary fusion in this problem setting.}\label{fig:layered_depthmap_convergence}
\end{figure}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_alpha.png}
  \caption{The energy minimization process for layered depthmap estimation with different $\alpha$ values. Multi-way fusion generally performs better than binary fusion, but the optimization becomes harder for using more ways in each step.}\label{fig:layered_depthmap_by_alpha}
\end{figure}

From the convergence plot of layered depth map estimation, we can see that, Fusion Move, Parallel Fusion Move, and FS-MF all stalk at a high energy state. The reason is binary fusion of solution proposals (either from others or self) is too limited to further decrease the energy due to the complexity of the problem itself. Only when multi-way fusion is used (in FS-SS and FS), it becomes possible for the energy to further decrease. This coincides with the observation in \cite{layered_depthmap} that binary fusion of proposal solutions is not as powerful as their subspace fusion which is a special form of multi-way fusion here. To further explore the effect of multi-way fusion, we use different $\alpha$ {1, 3, 7, 15} in FS model while keeping other parameters the same and plot the energy-time curve in figure \ref{fig:layered_depth_map_by_alpha}.

As shown in \ref{section:results}, the multi-way fusion and solution sharing enabled by our uniform framework play a key role for improving performance in different settings. For better understanding our framework, we examine the role played by each factor more closely by varying each factor while keeping others the same.

>>>>

\mysubsubsection{Layered depthmap estimation}

\noindent We have used ``ours\_1'' data in~\cite{layered_depthmap} for
the experiments. Figure~\ref{fig:layered_depthmap_convergence} shows
that Fusion Move, Parallel Fusion Move and Sf-MF all got stuck in local
minima, which is due to the lack of multi-way fusion.  Layered depthmap
estimation is a challenging problem with very large solution space. The
binary fusion of solution proposals is too restrictive to make any
improvements.  This coincides with the observation in
\cite{layered_depthmap} that binary fusion of proposal solutions is not
as powerful as their subspace fusion which is a special form of
multi-way fusion here. Lastly, solution sharing also plays an important
role for this challenging problem for exactly the same reason, as SF
performs much better than SF-SS.
%
%From the plot, we can see that, Fusion Move, Parallel Fusion Move, and
%SF-MF all stalk at a high energy state.
To further study the effects of multi-way fusion, we have varied the
value of $\alpha$ in controlling the number of solution proposals to be
fused in SF-SS model (See
Fig.~\ref{fig:layered_depthmap_by_alpha}). Note that we have used SF-SS
instead of SS to disable solution sharing and better observe the effects
of multi-way fusion.
% SF-SS model (disable solution sharing to
%better observe the effect of multi-way fusion) while keeping other
%parameters the same and plot the energy minimization process in figure
It is interesting to see that more multi-way fusion takes longer to
converge, but finds a lower energy state at the end.
%We can see that as the number of
%ways to fuse becomes larger, each fusion step takes longer time, but the
%chance of finding a lower energy state increases.

\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/layered_depthmap_convergence.png}
  \caption{Energy plots for the layered depthmap estimation
 problem. Both the multi-way fusion and the solution sharing are important
 for this challenging problem.}\label{fig:layered_depthmap_convergence}
\end{figure}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_alpha.png}
 \caption{Energy plots for different values of $\alpha$.
 More multi-way fusion takes longer to converge but finds a better
 solution at the end.}\label{fig:layered_depthmap_by_alpha}
\end{figure}

### 2016-03-14 paper/result_optical_flow.tex
yasu

% \hang{figure file missing}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/optical_flow_convergence.png}
  \caption{The energy minimization process for optical flow estimation of different methods. FS-MF has the best performance because of the solution sharing in early stage.}\label{fig:optical_flow_convergence}
\end{figure}
\begin{figure}[tb]
  \includegraphics[width=0.5\columnwidth]{figure/optical_flow_SF_MF_threads.png}
  \includegraphics[width=0.5\columnwidth]{figure/optical_flow_PFM_threads.png}
  \caption{Per thread energy. The left and right figures show the energy minimization process on each working thread of our method in SF-MF configuration and parallel fusion move, respectively.}\label{fig:optical_flow_by_threads}
\end{figure}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/optical_flow_by_beta.png}
  \caption{The energy minimization process for optical flow estimation with different $\beta$ values. Solution sharing generally makes energy minimization faster, but more solution sharing also means less time for exploring new solution proposals.}\label{fig:optical_flow_by_beta}
\end{figure}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/optical_flow_by_interval.png}
  \caption{The energy minimization process for optical flow estimation with different solution sharing frequency. Solution sharing generally makes energy minimization faster, but frequent solution sharing also means less time for exploring new solution proposals.}\label{fig:optical_flow_by_beta}\label{fig:optical_flow_by_interval}
\end{figure}

Figure \ref{fig:optical_flow_convergence} illustrates the convergence rate of three competing methods (alpha expansion, parallel alpha expansion, hierarchical fusion) against
our swarm fusion method. From the figure we can observe that, both conducting binary fusion, FS-MF finds lower energy faster than PFM. This is because some solution proposals are more effective than others, so once a thread grabs an effective solution proposal, it find a lower energy quickly. Since there is no solution sharing in PFM model, other threads cannot share this lower energy state, and keeps working on its own state. On the other hand, FS-MF allows solution sharing, so once a thread grabs an effective solution proposal and moves to a lower energy state, other threads can share this lower energy state. To further demonstrate what is happening here, we plot per thread energy in PFM and FS-MF in figure \ref{fig:optical_flow_by_threads}. As we can see from the plots, in PFM model, one thread finds lower energy state faster than others, while other threads keep working at their own energy state. But in FS-MF model, all threads exchange information about the lowest energy state and work on improving the lowest energy state together. So there are more chance of finding effective proposals faster. Since the solution for optical flow can be locally improved by each thread, the final merging of PFM can effectively fuse good local results in different threads together and achieve a similar energy state with FS-MF model. But since FS-MF model shares information in the middle, a final merging becomes less necessary. Same comparison holds for FS-SS and FS. The multi-way fusion is ineffective in this problem setting since solution proposals are relatively independant and fusing multiple solutions together using TRW-S~\cite{TRW-S} is less efficient than fusing them one by one using~\cite{QPBO}.

They are two factors influencing solution sharing: 1) \textit{the number of solutions to share} and 2) \textit{the solution sharing frequency}. Both factors are controlled by $\beta$. As mentioned in the section \label{optical_flow}, we use $\beta = 1$ once in every five iterations and use $\beta = 0$ for all other iterations. This means we share one solution in every five iterations. To further understand the effect of solution sharing, we did two other experiments for comparison. In one experiment, we use $\beta = {0, 1, 2, 3}$ in every five iterations and $\beta = 0$ for other iterations (when $\beta = 0$, it is same with PFM without final merging). While keeping all other factor same, we plot the energy minimization process in figure \ref{fig:optical_flow_by_beta}. As shown in the figure, energy generally decreases faster with solution sharing. But since we need to perform one fusion for sharing each solution, sharing more solution decreases efficiency in this problem setting. While sharing multiple solutions might be useful in some other problem setting as it means each thread can get more global information early. In another experiment, we change the number of iterations between two consecutive solution sharing iterations (the number of zero $\beta$ between two non-zero $\beta$) and plot the energy minimization process in figure \ref{fig:optical_flow_by_interval}. From this figure, we can see that although solution sharing generally speeds up the optimization process, sharing solution too frequently is not a good practice. This is because when we share solution frequently, we have less time for generating and fusing new proposals. A good choice of the solution sharing frequency depends on specific problem setting.

>>>>

\noindent
%
We have chosen the Dimetrodon image pair from the Middlebury flow
dataset~\cite{middlebury_flow}. Figure~\ref{fig:optical_flow_convergence}
shows the energy plots of the three competing methods, Fusion Move
(FM), parallel fusion move (PFM), and Hierarchical Fusion Move (HFM),
against our swarm fusion methods (SF-MF, SF-SS, SF). A key observation
is that SF-MF converges quicker and better than PAE. This is indeed the
benefits of solution sharing in our network. Optical flow is a more
difficult problem and many solution proposals are not effective.
The solution sharing (i.e., SF-MF) allows all the threads to exchange
effective solution proposal information in the middle of the
optimization.
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/optical_flow_convergence.png}
  \caption{Energy plots for optical flow estimation. SF-MF has the best
 performance due to its solution sharing strategy.}\label{fig:optical_flow_convergence}
\end{figure}
\begin{figure}[tb]
  \includegraphics[width=0.5\columnwidth]{figure/optical_flow_SF_MF_threads.png}
  \includegraphics[width=0.5\columnwidth]{figure/optical_flow_PFM_threads.png}
 \caption{Energy plots per thread for SF-MF (left) and Parallel Fusion
 Move (right).}\label{fig:optical_flow_by_threads}
\end{figure}
%
% This is because some solution proposals are more effective than others,
% so once a thread grabs an effective solution proposal, it find a lower
% energy quickly. Since there is no solution sharing in PFM model, other
% threads cannot share this lower energy state, and keeps working on its
% own state.
%
%On the other hand, SF-MF
%allows solution sharing, so once a thread grabs an effective solution
%proposal and moves to a lower energy state, other threads can share
%information about this lower energy state. In this manner, all threads
%contribute to further decrease of this low energy state. To further
%demonstrate what is happening here,
To further investigate the effectiveness of solution sharing,
Figure~\ref{fig:optical_flow_by_threads} shows the energy plots of PFM
and SF-MF per thread. As evident from the plot, in PFM, one thread found
a better solution than others, but other threads keep working
independently at higher energy states. SF-MF, on the other hand,
exchanges solutions all the time, and every thread is making an effective
work in improving the solution.
%As we can see from the plots, in PFM model, one thread finds lower
%energy state faster than others, while other threads keep working at
%their own energy state. But in SF-MF model, all threads exchange
%information about the lowest energy state frequently and work on
%improving the lowest energy state together. Since the solution for
%optical flow can be locally improved by each thread, the final merging
%of PFM can effectively fuse good local results in different threads
%together and achieve a similar energy state with SF-MF model. But as
%SF-MF model shares information in the middle, a final merging becomes
%less necessary.
Another key finding from Fig.~\ref{fig:optical_flow_convergence} is that
SF is slower than SF-MF. Our analysis is that multi-way fusion is
inefficient in this problem setting, since solution proposals are
relatively independent and fusing the solution space would not gain much
benefit. It rather loses performance against QPBO~\cite{QPBO} due to the
overhead of TRW-S.

There are two factors influencing solution sharing: 1) \textit{the number
of solutions to share} and 2) \textit{the frequency of solution
sharing}. Both factors are controlled by $\beta$. As mentioned in
Section \label{optical_flow}, we have used $\beta = 1$ once in every five
iterations ($\beta = 0$ for other iterations): We share solutions once in
every five iterations.  To further understand the effects of solution
sharing, we did two more experiments. First, we set $\beta$ to 0, 1, 2,
or 3 in every five iterations,
% (when $\beta = 0$, it is the same with PFM without final merging).
while keeping all other parameters the same (See
Fig.~\ref{fig:optical_flow_by_beta}).  Second, we change the number of
iterations $k$ between the two consecutive solution sharing iterations
(See Fig.~\ref{fig:optical_flow_by_interval}).  The first experiment
revealed that the converegence was faster with the solution sharing than
without the solution sharing, regarless of $\beta$.
However, too much solution sharing slows down the converence, and
$\beta=1$ is the sweet spot for this problem.
%
% , energy generally
% decreases faster with solution sharing. But since we need to perform one
% fusion for sharing each solution, sharing more solution decreases
% efficiency in this problem setting. While sharing multiple solutions
% might be useful in some other problem setting as it means each thread
% can get more global information early.
%
The second experiment has revealed that too frequent solution sharing
harms the converengece, simply because we have less time generating more
proposals and exploring the solution space.
% From this figure, we can see that
% although solution sharing generally speeds up the optimization process,
% sharing solution too frequently is not a good practice. This is because
% when we share solution frequently, we have less time for generating and
%fusing new proposals.
Optimal parameter setting depends on each problem setting.
%A good choice of the solution sharing frequency depends on specific
%problem setting.
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/optical_flow_by_beta.png}
  \caption{Energy plots for optical flow with different values of
  $\beta$. Solution sharing achieves better convergence. However, too
  much solution sharing slows down the converence, as it reduces the
 time for exploration.}\label{fig:optical_flow_by_beta}
\end{figure}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/optical_flow_by_interval.png}
  \caption{Energy plots for optical flow with different solution sharing
  frequencies. Solution sharing is critical, but too frequent solution
  sharing (less $k$) slows down the convergence.}
 \label{fig:optical_flow_by_beta}\label{fig:optical_flow_by_interval}
\end{figure}

### 2016-03-14 paper/result_stereo.tex
Hang
yasu

We performed our experiments on the half-size Book sequence from Middlebury stereo
datasets.~\cite{middlebury_stereo}. We use 7 images with the
resolution of $695\times555$ and optimize for 256 disparity labels. We
recoreded both single thread energy and system energy (minimum energy
so far from all threads) against time.

\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/stereo_global.eps}
  \caption{The energy minimization process of difference parallel systems.}
  \label{fig:stereo_global}
\end{figure}

\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/stereo_threads.png}
  \caption{Per thread energy. The left and right figures show the
    energy minimization process on each working thread of our method
    in SF-MF configuration and parallel $\alpha$-expansion method,
    respectively. The energy is in $\log$ scale}
  \label{fig:stereo_threads}
\end{figure}

Figure \ref{fig:stereo_global} shows the energy minimization process
against time. In this experiment, both PAE and SF-MF converge faster
than sequential method. However, since fusing solutions with multiple
labels by QPBO is slower than a single $\alpha$-expansion, PAE method
reaches convergence faster than SF-MF. Architectures with multiway
fusion, e.g. SF and SF-SS perform worse than PAE and SF-MF, because
the TRWS algorihtm used in multiway fusion is slower than multiple
$\alpha$-expansion. Finally, the line of hierarchy fusion only makes
jump when fusing on root node of the tree. This is because any fusion
step on non-root nodes only have partial label information.

Figure \ref{fig:stereo_threads} shows the per-thread energy
minimization process in SF-MF and PAE. The per-thread energy in SF-MF
architecture decreases more uniformly than that of PAE. In the
scenario where we need to query the best solution so far before the
whole optimization converges, SF-MF architecture is a better choice.

For a easy optimization problem as shown in this section, our full
architecture with solution sharing and multiway fusion actually makes
convergence slower by adopting sophisticated algorihtm and introducing
multi-threading overhead. However, we can easily configure the
architecture to make it better fit the problem, e.g. turn off multiway
fusion and/or solution sharing.

\hang{The end of stereo experiment......}

>>>>

\noindent We have chosen 7 images with the resolution of $695\times555$
from the Book sequence of Middlebury stereo dataset for our
experiment~\cite{middlebury_stereo}. The number of disparity labels is
set to 256.
%
Since the order of labels is important for the expansion techniques,
we have picked a random order to avoid any bias.
%
% In PAE, SF-MF, SF-SS and SF algorithms, the proposal generator in each
% thread can only generate constant-label proposals within a evenly split
% subset of all labels.

Figure~\ref{fig:stereo_global} compares the converegence rate of the
competing methods. Note that we define the energy of a multi-threading
system to be the energy of the best solution found so far.
%
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/stereo_global.png}
 \caption{Energy plots for the stereo problem. The energy is in the
 log scale. For a multi-threading algorithm, the energy at any given
 moment is defined to be the best solution so far.} \label{fig:stereo_global}
\end{figure}
%
One unusual outcome is that Sequential Alpha Expansion and Parallel
Alpha Expansion (PAE) have the same convergence speed, indicating that
the stereo problem is a very easy one. This is well known in a community
and this fact was rather expected. Our approaches with multi-way fusion
(SF-SS or SF) are the slowest kind, because the TRW-S for multi-way
fusion is slower than multiple Alpha Expansion steps, and this stereo
problem is too easy to gain benefits through mulit-way fusion.
%
%Another interesting observation is that the Hierarchical Fusion can
%achieve good energy only when they merge solutions at the top of the
%tree.
%
%  both PAE and SF-MF converge faster
% than sequential method. However, since fusing solutions with multiple
% labels by QPBO is slower than a single $\alpha$-expansion, PAE method
%
% Finally, the line of hierarchy fusion only makes
% jump when fusing on root node of the tree. This is because any fusion
% step on non-root nodes only have partial label information.
%We recoreded both single thread energy and system energy against
%time.
%
Figure \ref{fig:stereo_threads} shows the energy plot per thread
for SF-MF (ours) and PAE. The graph for PAE again confirms that the
stereo is an easy problem, because all the threads are quickly
converging to a solution before the final sequential fusion.
%shows the per-thread energy
%minimization process in SF-MF and PAE. The per-thread energy in SF-MF
%architecture decreases more uniformly than that of PAE. In the
%scenario where we need to query the best solution so far before the
%whole optimization converges, SF-MF architecture is a better choice.
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/stereo_threads.png}
  \caption{\yasu{Put a text in the figures showing which one is
  SF-MF(ours) and which one is parallel alpha expansion} Per thread
  energy. The left and right figures show the energy minimization
  process on each working thread of our method in SF-MF configuration
  and parallel $\alpha$-expansion method, respectively. The energy is in
  $\log$ scale} \label{fig:stereo_threads}
\end{figure}

For an easy optimization problem such as stereo with strong unary terms
and submodular pairwise terms, our full architecture with solution
sharing and multiway fusion actually makes convergence slower due to the
overhead of fusion and multi-threading.

% over-sophisticated fusion algorihtm and multi-threading
% overhead. However, we can easily configure the architecture to make it
% better fit the problem, e.g. turn off multiway fusion and/or solution
% sharing.

% We define the energy of
% a parallel optimization system at a certain time as the minimum energy
% of all threads at that time.

### 2016-03-14 paper/results.tex
another pass
yasu

\section{Experimental results}
\label{section:results}
We have implemented the algorithms with multithreading supporting from
C++ 11 and conducted the experiments on Linux PCs with Intel Core i7
4790 processor with 4 cores. We have used the Graph-cuts optimization
code written by Veksler, using the libraries provided by Boykov and
Kolmogorov~\cite{middlebury_mrf,alpha_expansion,what_energy_can_be_min_by_gc,mrf_experimental}.
% [2] Fast Approximate Energy Minimization via Graph Cuts.
%         Y. Boykov, O. Veksler, and R. Zabih.
%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
%         (PAMI), vol. 23, no. 11, pages 1222-1239, November 2001.  
%
%     [3] What Energy Functions can be Minimized via Graph Cuts?
%         V. Kolmogorov and R. Zabih. 
%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
%         (PAMI), vol. 26, no. 2, pages 147-159, February 2004. 
%         An earlier version appeared in European Conference on Computer
%         Vision (ECCV), May 2002.
%
%     [4] An Experimental Comparison of Min-Cut/Max-Flow Algorithms for
%         Energy Minimization in Vision. 
%         Y. Boykov and Vladimir Kolmogorov.
%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
%         (PAMI), vol. 26, no. 9, pages 1124-1137, September 2004. 
We have used the QPBO and TRW-S implementations by
Kolmogorov~\cite{QPBO, TRW-S_implementation}.

To evaluate the effectness of different parallel structures, we plot
the energy minimization process against time. We define the energy of
a parallel optimization system at a certain time as the minimum energy
of all threads at that time.

@@

>>>>

\section{Experimental results}
\label{section:results} We have implemented the algorithms with
multi-threading support from C++ 11, and conducted the experiments on
Linux PCs with Intel Core i7 4790 processor with 4 cores. We have used
the Graph-cuts optimization code written by Veksler, using the libraries
provided by Boykov and
Kolmogorov~\cite{middlebury_mrf,alpha_expansion,what_energy_can_be_min_by_gc,mrf_experimental}.
% [2] Fast Approximate Energy Minimization via Graph Cuts.
%         Y. Boykov, O. Veksler, and R. Zabih.
%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
%         (PAMI), vol. 23, no. 11, pages 1222-1239, November 2001.  
%
%     [3] What Energy Functions can be Minimized via Graph Cuts?
%         V. Kolmogorov and R. Zabih. 
%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
%         (PAMI), vol. 26, no. 2, pages 147-159, February 2004. 
%         An earlier version appeared in European Conference on Computer
%         Vision (ECCV), May 2002.
%
%     [4] An Experimental Comparison of Min-Cut/Max-Flow Algorithms for
%         Energy Minimization in Vision. 
%         Y. Boykov and Vladimir Kolmogorov.
%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
%         (PAMI), vol. 26, no. 9, pages 1124-1137, September 2004. 
We have used the QPBO and TRW-S implementations by
Kolmogorov~\cite{QPBO, TRW-S_implementation}. We now look at our
experimental results for the three problems one by one.

% To evaluate the effectness of different parallel structures, we plot
% the energy minimization process against time. We define the energy of
% a parallel optimization system at a certain time as the minimum energy
% of all threads at that time.

@@

As shown in the above problem settings, the solution sharing and multi-way fusion enabled by our uniform framework play a key role for improving performance in different problem settings.

### 2016-03-14 paper/stereo.tex
yasu

We compare SF against competing approaches over three problems in
Computer Vision. SF framework has high degrees of freedom and the
challenge is to properly quantify the contributions of various
algorithmic aspects. For this purpose, we have used the three SF
architectures illustrated in Fig.~\ref{fig:model}.
%% For some problems, we have further limited the capabilities of SF
%% on purpose, to enable effective and fair comparative
%% evaluations. We now explain the details of the three problems.

>>>>

We compare SF against competing approaches over three problems in
Computer Vision, namely, stereo, optical flow, and layered depthmap
estimation.

% SF framework has high degrees of freedom and the
%challenge is to properly quantify the contributions of various
%algorithmic aspects.

%For this purpose, we have used the three SF architectures illustrated in
%Fig.~\ref{fig:model}.
%% For some problems, we have further limited the capabilities of SF
%% on purpose, to enable effective and fair comparative
%% evaluations. We now explain the details of the three problems.
